Comparison of Fast, Hybird Imaging Architectures for Multi-scale, Hierarchical Aperture Arrays

### 2024-06-18 ms.tex
Add ms.bbl, scripts in /bin to repo, rename figures

\begin{figure}
% \includegraphics[width=\linewidth]{figures/flops_calc.pdf}
\includegraphics[width=\linewidth]{figures/flops_calc_abridged.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{A hybrid multi-stage architecture for aperture arrays consisting of stations each of which contain multiple elements. Black arrows indicate pathways where the data is in the form of electric fields with phase coherence. Gray arrows indicate pathways where the signal is a ``squared'' or a correlated quantity with no absolute but only relative phase information. At the top are intra-station architectures, namely, BF, correlator, and EPIC. The top box denotes intra-station imaging options. The bottom box denotes inter-station imaging architectures which take the coherent outputs from multiple stations with intra-station voltage beamformer and EPIC architectures dpeployed on each of them. 
\label{fig:hybrid-architectures-cost-schematic}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_beamformer_dft_cost_analysis_SKA1-low.pdf}
{figures/1D_beamformer_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the voltage beamforming architecture at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I} station (cyan lines). The beamforming cost in Equation~(\ref{eqn:intra-station-pol-hol-img-expl}) denoted by black dashed lines dominates the squaring (pink dot-dashes) and temporal averaging (blue dot-dashes) costs in Equation~(\ref{eqn:intra-station-opt-pol-img-outprod}). 
\label{fig:1D-incoherent-compcost-BF-LAMBDA-I}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/multidim_beamformer_dft_cost_analysis_SKA1-low.pdf}
{figures/multidim_beamformer_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{A multi-dimensional covariant view of the net computational cost density function over the station parameters for the voltage beamforming architecture at the station level by varying two parameters at a time while fixing the rest at the nominal values of a \texttt{LAMBDA-I} station shown in grey dashed lines. The empty portions in the panels denote parts of parameter space physically impossible to sample given the constraints of the station parameters. Contours corresponding to the color scale are shown in cyan. 
\label{fig:multidim-incoherent-compcost-BF-LAMBDA-I}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.99\linewidth]
% {figures/1D_epic_cost_analysis_SKA1-low.pdf}
{figures/1D_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the EPIC architecture at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I} station (cyan lines). The spatial FFT cost in Equation~(\ref{eqn:intra-station-pol-hol-img-epic})
  % {eqn:intra-station-pol-hol-img-epic-LA}
  denoted by black dashed lines dominates the squaring (pink dot-dashes) and temporal averaging (blue dot-dashes) costs in Equation~(\ref{eqn:intra-station-opt-pol-img-outprod}).
  % {eqn:intra-station-opt-polarimetric-direct-img-LA}
  The gridding operation (black dotted lines) in Equation~(\ref{eqn:intra-station-pol-hol-img-epic})
  % {eqn:intra-station-pol-hol-img-epic-LA}
  contributes even lesser to the cost budget. 
\label{fig:1D-incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][Covariant cost density of EPIC architecture \label{fig:multidim-incoherent-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_cost_analysis_SKA1-low.pdf}
{figures/multidim_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Covariant cost of EPIC architecture relative to VBF architecture \label{fig:multidim-incoherent-relative-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_epic_relative_cost_analysis_LAMBDA-I.pdf}
} 
\caption{(Left): Two-dimensional slices of the computational cost per station per voxel for coherent-incoherent imaging using station-level EPIC. Because the spatial FFT dominates the overall cost budget, the computational cost density is relatively insensitive to $N_\textrm{a/s}$, $D_\textrm{s}$, and $D_\textrm{a}$. (Right): Ratio of computational cost of EPIC to voltage beamforming. For $N_\textrm{a/s}\gtrsim 100$, EPIC has a significant advantage over voltage beamforming Cyan contours indicate nominal values for a \texttt{LAMBDA-I} station. \label{fig:incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_xcor_dft_cost_analysis_SKA1-low.pdf}
{figures/1D_xcor_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the correlator beamforming architecture (XBF) at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I}, \texttt{SKA-low-core}, and \texttt{SKA-low} stations (cyan lines). The two-dimensional DFT (dashed lines) dominates the cost for the chosen \texttt{LAMBDA-I} parameters at an imaging cadence of $t_\textrm{acc}=1$~ms over correlation (double dot-dashed) and temporal averaging of the correlations (dot-dashed).
% The spatial FFT cost in Equation~(\ref{eqn:intra-station-pol-hol-img-epic-LA}) denoted by black dashed lines dominates the squaring (pink dot-dashes) and temporal averaging (blue dot-dashes) costs in Equation~(\ref{eqn:intra-station-opt-polarimetric-direct-img-LA}). The gridding operation (black dotted lines) in Equation~(\ref{eqn:intra-station-pol-hol-img-epic-LA}) contributes even lesser to the cost budget. 
\label{fig:1D-incoherent-compcost-XBF-LAMBDA-I}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][Covariant cost density of XBF architecture \label{fig:multidim-incoherent-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Covariant cost of XBF architecture relative to VBF architecture \label{fig:multidim-incoherent-relative-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_dft_relative_cost_analysis_LAMBDA-I.pdf}
}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using a DFT of station-level cross-correlations for \texttt{LAMBDA-I}, \texttt{SKA-low-core}, and \texttt{SKA-low} station parameters (dashed gray lines). Cyan lines denote contours of the colour scale in logarithmic increments. (Right): Same as the left but relative to a voltage beamformer architecture. The computational cost density is dominated by the two-dimensional DFT cost for $t_\textrm{acc}=1$~ms, and is lower than that of voltage beamforming for $N_\textrm{a/s}\lesssim 100$ while getting more expensive with increasing $N_\textrm{a/s}$. \label{fig:incoherent-compcost-XBF-LAMBDA-I}}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_xcor_fft_cost_analysis_SKA1-low.pdf}
{figures/1D_xcor_fft_per_pixel_cost_analysis_LAMBDA-I.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the correlator FFT architecture (XFFT) at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I}, \texttt{SKA-low-core}, and \texttt{SKA-low} stations (cyan lines). The correlator / X-engine (double dot- dashed lines) and gridding (dotted lines) dominate the cost for the chosen \texttt{LAMBDA-I} parameters at an imaging cadence of $t_\textrm{acc}=1$~ms over the temporal averaging (dot dahsed lines) and two-dimensional FFT (dashed lines).
\label{fig:1D-incoherent-compcost-XFFT-LAMBDA-I}}
\end{figure}

\begin{figure*}
\centering
\subfloat[][Covariant cost density of XFFT architecture \label{fig:multidim-incoherent-compcost-XFFT-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_fft_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_fft_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Covariant cost of XFFT architecture relative to VBF architecture \label{fig:multidim-incoherent-relative-compcost-XFFT-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_fft_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_fft_relative_cost_analysis_LAMBDA-I.pdf}
}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using an FFT of station-level cross-correlations for . Cyan contours  \label{fig:incoherent-compcost-XFFT-LAMBDA-I}}
\end{figure*}

@@

\begin{figure}
\centering
\subfloat[][Station imaging compute cost densities for \texttt{LAMBDA-I}, \texttt{SKA1-low-core}, and \texttt{SKA1-low}. \label{fig:1D-incoherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
% {figures/1D_compcost_analysis_SKA1-low.pdf}
{figures/1D_per_pixel_compcost_analysis_LAMBDA-I.pdf}
} \\
\subfloat[][Station imaging compute cost densities for \texttt{CASPA}.\label{fig:1D-incoherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
% {figures/1D_relative_compcost_analysis_SKA1-low.pdf}
{figures/1D_per_pixel_compcost_analysis_CASPA.pdf}
} \\
\subfloat[][Station imaging compute cost densities for \texttt{FarView}. \label{fig:1D-incoherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
% {figures/1D_relative_compcost_analysis_SKA1-low.pdf}
{figures/1D_per_pixel_compcost_analysis_FarView.pdf}
}
\caption{Computational cost densities of different station level imaging architectures for (a) \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}, (b) \texttt{CASPA}, and (c) \texttt{FarView}. In each subpanel, all parameters are fixed at the array's nominal value (cyan line) except the parameter shown on the $x$-axis. For \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}, the EPIC architecture is found to be most efficient computationally. For \texttt{CASPA}, EPIC is more efficient than other architectures when imaging cadence is $t_\textrm{acc}\lesssim 1-5$~ms, while XFFT is more efficient for $t_\textrm{acc}\gtrsim 5-10$~ms. For \texttt{FarView}, EPIC and XFFT are equally efficient when the cadence is $t_\textrm{acc}\approx 1$~ms, while EPIC and XFFT are advantageous for cadences faster and slower, respectively, than 1~ms.  \label{fig:1D-incoherent-compcost}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][\texttt{LAMBDA-I} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_LAMBDA-I.pdf}
} \\
\subfloat[][\texttt{SKA1-Low-core} \label{fig:1D-coherent-compcost-SKA1-low-core}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low-core.pdf}
} \\
\subfloat[][\texttt{SKA1-Low} \label{fig:1D-coherent-compcost-SKA1-low}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low.pdf}
} 
\caption{One-dimensional slices of the computational cost density for (a) \texttt{LAMBDA-I}, (b) \texttt{SKA-low-core}, and (c) \texttt{SKA-low} using  coherent imaging at intra- and inter-station levels via VBF (gray) and EPIC (black) for intra-station processing, and VBF (dotted), EPIC (solid), XBF (dashed), and XFFT (dot-dashed) for inter-station processing of data. \label{fig:1D-coherent-compcost-a}}
\end{figure*}

\begin{figure*}\ContinuedFloat
\subfloat[][\texttt{CASPA} \label{fig:1D-coherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_CASPA.pdf}
} \\
\subfloat[][\texttt{FarView} \label{fig:1D-coherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_FarView.pdf}
}
\caption{Contd. Same as above but for (d) \texttt{CASPA}, and (e) \texttt{FarView} \label{fig:1D-coherent-compcost-b}}
\end{figure*}

>>>>

\begin{figure}
\includegraphics[width=\linewidth]
  % {figures/flops_calc_abridged.pdf}
{fig_01.pdf}
\caption{A hybrid multi-stage architecture for aperture arrays consisting of stations each of which contain multiple elements. Black arrows indicate pathways where the data is in the form of electric fields with phase coherence. Gray arrows indicate pathways where the signal is a ``squared'' or a correlated quantity with no absolute but only relative phase information. At the top are intra-station architectures, namely, BF, correlator, and EPIC. The top box denotes intra-station imaging options. The bottom box denotes inter-station imaging architectures which take the coherent outputs from multiple stations with intra-station voltage beamformer and EPIC architectures dpeployed on each of them. 
\label{fig:hybrid-architectures-cost-schematic}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_beamformer_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
{fig_02.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the voltage beamforming architecture at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I} station (cyan lines). The beamforming cost in Equation~(\ref{eqn:intra-station-pol-hol-img-expl}) denoted by black dashed lines dominates the squaring (pink dot-dashes) and temporal averaging (blue dot-dashes) costs in Equation~(\ref{eqn:intra-station-opt-pol-img-outprod}). 
\label{fig:1D-incoherent-compcost-BF-LAMBDA-I}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/multidim_beamformer_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
{fig_03.pdf}
\caption{A multi-dimensional covariant view of the net computational cost density function over the station parameters for the voltage beamforming architecture at the station level by varying two parameters at a time while fixing the rest at the nominal values of a \texttt{LAMBDA-I} station shown in grey dashed lines. The empty portions in the panels denote parts of parameter space physically impossible to sample given the constraints of the station parameters. Contours corresponding to the color scale are shown in cyan. 
\label{fig:multidim-incoherent-compcost-BF-LAMBDA-I}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.99\linewidth]
% {figures/1D_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
{fig_04.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the EPIC architecture at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I} station (cyan lines). The spatial FFT cost in Equation~(\ref{eqn:intra-station-pol-hol-img-epic})
  % {eqn:intra-station-pol-hol-img-epic-LA}
  denoted by black dashed lines dominates the squaring (pink dot-dashes) and temporal averaging (blue dot-dashes) costs in Equation~(\ref{eqn:intra-station-opt-pol-img-outprod}).
  % {eqn:intra-station-opt-polarimetric-direct-img-LA}
  The gridding operation (black dotted lines) in Equation~(\ref{eqn:intra-station-pol-hol-img-epic})
  % {eqn:intra-station-pol-hol-img-epic-LA}
  contributes even lesser to the cost budget. 
\label{fig:1D-incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][Covariant cost density of EPIC architecture \label{fig:multidim-incoherent-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
{fig_05a.pdf}  
}
\subfloat[][Covariant cost of EPIC architecture relative to VBF architecture \label{fig:multidim-incoherent-relative-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_relative_cost_analysis_LAMBDA-I.pdf}
{fig_05b.pdf}
} 
\caption{(Left): Two-dimensional slices of the computational cost per station per voxel for coherent-incoherent imaging using station-level EPIC. Because the spatial FFT dominates the overall cost budget, the computational cost density is relatively insensitive to $N_\textrm{a/s}$, $D_\textrm{s}$, and $D_\textrm{a}$. (Right): Ratio of computational cost of EPIC to voltage beamforming. For $N_\textrm{a/s}\gtrsim 100$, EPIC has a significant advantage over voltage beamforming Cyan contours indicate nominal values for a \texttt{LAMBDA-I} station. \label{fig:incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_xcor_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
{fig_06.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the correlator beamforming architecture (XBF) at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I}, \texttt{SKA-low-core}, and \texttt{SKA-low} stations (cyan lines). The two-dimensional DFT (dashed lines) dominates the cost for the chosen \texttt{LAMBDA-I} parameters at an imaging cadence of $t_\textrm{acc}=1$~ms over correlation (double dot-dashed) and temporal averaging of the correlations (dot-dashed).
% The spatial FFT cost in Equation~(\ref{eqn:intra-station-pol-hol-img-epic-LA}) denoted by black dashed lines dominates the squaring (pink dot-dashes) and temporal averaging (blue dot-dashes) costs in Equation~(\ref{eqn:intra-station-opt-polarimetric-direct-img-LA}). The gridding operation (black dotted lines) in Equation~(\ref{eqn:intra-station-pol-hol-img-epic-LA}) contributes even lesser to the cost budget. 
\label{fig:1D-incoherent-compcost-XBF-LAMBDA-I}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][Covariant cost density of XBF architecture \label{fig:multidim-incoherent-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
{fig_07a.pdf}
}
\subfloat[][Covariant cost of XBF architecture relative to VBF architecture \label{fig:multidim-incoherent-relative-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_relative_cost_analysis_LAMBDA-I.pdf}
{fig_07b.pdf}
}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using a DFT of station-level cross-correlations for \texttt{LAMBDA-I}, \texttt{SKA-low-core}, and \texttt{SKA-low} station parameters (dashed gray lines). Cyan lines denote contours of the colour scale in logarithmic increments. (Right): Same as the left but relative to a voltage beamformer architecture. The computational cost density is dominated by the two-dimensional DFT cost for $t_\textrm{acc}=1$~ms, and is lower than that of voltage beamforming for $N_\textrm{a/s}\lesssim 100$ while getting more expensive with increasing $N_\textrm{a/s}$. \label{fig:incoherent-compcost-XBF-LAMBDA-I}}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_xcor_fft_per_pixel_cost_analysis_LAMBDA-I.pdf}
{fig_08.pdf}
\caption{A breakdown of the computational cost density function over the station parameters for the correlator FFT architecture (XFFT) at the station level. Each panel shows the variation with the respective parameter keeping the rest fixed at the characteristic values of the \texttt{LAMBDA-I}, \texttt{SKA-low-core}, and \texttt{SKA-low} stations (cyan lines). The correlator / X-engine (double dot- dashed lines) and gridding (dotted lines) dominate the cost for the chosen \texttt{LAMBDA-I} parameters at an imaging cadence of $t_\textrm{acc}=1$~ms over the temporal averaging (dot dahsed lines) and two-dimensional FFT (dashed lines).
\label{fig:1D-incoherent-compcost-XFFT-LAMBDA-I}}
\end{figure}

\begin{figure*}
\centering
\subfloat[][Covariant cost density of XFFT architecture \label{fig:multidim-incoherent-compcost-XFFT-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_fft_per_pixel_cost_analysis_LAMBDA-I.pdf}
{fig_09a.pdf}
}
\subfloat[][Covariant cost of XFFT architecture relative to VBF architecture \label{fig:multidim-incoherent-relative-compcost-XFFT-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_fft_relative_cost_analysis_LAMBDA-I.pdf}
{fig_09b.pdf}
}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using an FFT of station-level cross-correlations for . Cyan contours  \label{fig:incoherent-compcost-XFFT-LAMBDA-I}}
\end{figure*}

@@

\begin{figure}
\centering
\subfloat[][Station imaging compute cost densities for \texttt{LAMBDA-I}, \texttt{SKA1-low-core}, and \texttt{SKA1-low}. \label{fig:1D-incoherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
% {figures/1D_per_pixel_compcost_analysis_LAMBDA-I.pdf}
{fig_10a.pdf}
} \\
\subfloat[][Station imaging compute cost densities for \texttt{CASPA}.\label{fig:1D-incoherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
% {figures/1D_per_pixel_compcost_analysis_CASPA.pdf}
{fig_10b.pdf}
} \\
\subfloat[][Station imaging compute cost densities for \texttt{FarView}. \label{fig:1D-incoherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
% {figures/1D_per_pixel_compcost_analysis_FarView.pdf}
{fig_10c.pdf}
}
\caption{Computational cost densities of different station level imaging architectures for (a) \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}, (b) \texttt{CASPA}, and (c) \texttt{FarView}. In each subpanel, all parameters are fixed at the array's nominal value (cyan line) except the parameter shown on the $x$-axis. For \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}, the EPIC architecture is found to be most efficient computationally. For \texttt{CASPA}, EPIC is more efficient than other architectures when imaging cadence is $t_\textrm{acc}\lesssim 1-5$~ms, while XFFT is more efficient for $t_\textrm{acc}\gtrsim 5-10$~ms. For \texttt{FarView}, EPIC and XFFT are equally efficient when the cadence is $t_\textrm{acc}\approx 1$~ms, while EPIC and XFFT are advantageous for cadences faster and slower, respectively, than 1~ms.  \label{fig:1D-incoherent-compcost}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][\texttt{LAMBDA-I} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
% {figures/1D_coherent_per_pixel_compcost_analysis_LAMBDA-I.pdf}
{fig_11a.pdf}
} \\
\subfloat[][\texttt{SKA1-Low-core} \label{fig:1D-coherent-compcost-SKA1-low-core}]
{\includegraphics[width=\textwidth]
% {figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low-core.pdf}
{fig_11b.pdf}
} \\
\subfloat[][\texttt{SKA1-Low} \label{fig:1D-coherent-compcost-SKA1-low}]
{\includegraphics[width=\textwidth]
% {figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low.pdf}
{fig_11c.pdf}
} 
\caption{One-dimensional slices of the computational cost density for (a) \texttt{LAMBDA-I}, (b) \texttt{SKA-low-core}, and (c) \texttt{SKA-low} using  coherent imaging at intra- and inter-station levels via VBF (gray) and EPIC (black) for intra-station processing, and VBF (dotted), EPIC (solid), XBF (dashed), and XFFT (dot-dashed) for inter-station processing of data. \label{fig:1D-coherent-compcost-a}}
\end{figure*}

\begin{figure*}\ContinuedFloat
\subfloat[][\texttt{CASPA} \label{fig:1D-coherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
% {figures/1D_coherent_per_pixel_compcost_analysis_CASPA.pdf}
{fig_11d.pdf}
} \\
\subfloat[][\texttt{FarView} \label{fig:1D-coherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
% {figures/1D_coherent_per_pixel_compcost_analysis_FarView.pdf}
{fig_11e.pdf}
}
\caption{Contd. Same as above but for (d) \texttt{CASPA}, and (e) \texttt{FarView} \label{fig:1D-coherent-compcost-b}}
\end{figure*}
